Novel crystallization pathway\\and formation of ``colloidal rain'' during viscoelastic phase separation

### 2015-09-15 crystal-gel/crystal_gel_letter.tex
Include fig:phase_separation

\begin{figure*}[!t]
 \centering
 \includegraphics[width=8cm]{./oldfig/fig1b.pdf}
 \includegraphics[width=8cm]{./oldfig/fig1b.pdf}
 \includegraphics[width=8cm]{./oldfig/fig3c}
 \includegraphics[width=8cm]{./oldfig/fig3b}
 % fig1b.pdf: 687x479 pixel, 72dpi, 24.24x16.90 cm, bb=0 0 687 479
 \caption{{\bf Different routes of viscoelastic phase separation.}
 \textbf{a,} {\color{blue}Phase diagram.}
 \textbf{b,} Radius of gyration ($R_g$) as a function of cluster size ($s$) for all state points at percolation. The
 dashed line represents the exponent of the random gelation universality class.
 \textbf{c,} Structure factors for the late stages of the gelation process. Calculation of the structure factor is done with the Hanning window function,  to minimize boundary effects.
 \textbf{d,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle.
 Different lines represent the different state points.
 }
 \label{fig:phase_separation}
\end{figure*}

>>>>

\begin{figure*}[!t]
 \centering
 \includegraphics{./fig/phase_separation.pdf}
 \caption{{\bf Different routes of viscoelastic phase separation.}
 \textbf{a,} Phase diagram. Dashed lines are fluid-solid equilibrium coexistence boundaries. The continuous line is the gas side of the metastable gas-liquid spinodal region with the black diamond marking the critical point. The other symbols are the experimental points, consistently used in all panels.
 \textbf{b,} Radius of gyration ($R_g$) as a function of cluster size ($s$) for all state points at percolation. The
 gray line represents the fractal dimension of the random gelation universality class.
 \textbf{c,} Structure factors for the late stages of the gelation process. The gray and black lines represents respectively random gelation and compact fractal dimensions.
 \textbf{d,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle \textcolor{blue}{at late stage?}. Horizontal lines stress the value at 12 neighbours.
 }
 \label{fig:phase_separation}
\end{figure*}
